Knowledge Representation for Service Robots: Supply and Demand

### 2012-05-14 krs-survey.tex
Completed perspective taking theroy of mind

A \emph{contingent} proposition is defined as neither always true (a tautology)
nor always false (a contradiction) in every possible world. In knowledge
representation systems for robotics that support logical modality,
interpretations are often initialised with a common set of initial beliefs
(like common-sense knowledge). This initial common knowledge is hence true in
every possible worlds for the robot, and thus does not belong to the contingent
knowledge.

Alternative mental models may be used to represent different (possibly
hypothetical or even imaginary) views on the world, from the robot own
perspective, or from persepectives of other agents, as computed by the robot.

provide explicit ways to model other point of view
on the world. This ability is often referred as the \emph{perspective taking}
ability.

>>>>

A \emph{contingent} proposition is defined as neither always true (a tautology)
nor always false (a contradiction) in every possible world. In knowledge
representation systems for robotics that support logical modality,
interpretations are often initialised with a common set of initial beliefs
(like common-sense knowledge). This initial common knowledge is hence true in
every possible worlds for the robot, and thus does not belong to its contingent
knowledge.

Logical modality allows to implement alternative mental models. They may be
used to represent different (possibly hypothetical or even imaginary) views on
the world, from the robot own perspective, or from other persepectives computed
by the robot.

The representation of the mental perspective of other agents has a particular
importance in human-robot interaction. It relies first on the ability to view
the world from a standpoint which is not \emph{egocentric}. This cognitive
ability is referred as \emph{perspective taking} (see
Flavell~\cite{Flavell1992} and Tversky~\cite{Tversky1999} for the psychological
grounds of perspective taking, itself originated in Piaget's work on cognitive
development, as remembered by Flavell), and has been studied by
infants~\cite{Moll2006} and robots as well~\cite{Trafton2005, Breazeal2006,
Ros2010}.

The idea of a \emph{theory of mind}~\cite{Premack1978} emerges from the
perspective taking ability. It can be defined as the ability for one to
understand and acknowledge that other intelligent agents can have their own
mental state (that includes beliefs, intents, desires, knowledge) that is
possibly different from one's own.

\begin{figure}
        \centering
        \includegraphics[width=0.9\columnwidth]{sally_ann.pdf}
        \caption{The standard ``Sally and Ann'' false-beliefs experiment, taken from~\cite{Leslie2000}.}
        \label{fig|sally-ann}
\end{figure}

Perceiving and understanding other's \emph{attention} has been identified as
essential to the development of a theory of mind by
Baron-Cohen~\cite{Baron-Cohen1985, Leslie2000}. In
robotics~\cite{Scassellati2002}
